---
title: "How to use farspractise"
author: "Zsuzsanna Ortutay"
date: "2017-03-17"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The farspractise package allows you to analyze data about fatal accidents by using the Fatality Analysis Reporting Sysetm from the US National Highway Traffic Safety Administration.

## Functions

The package contains 5 functions from which *fars_summarize_years()* prepares  a report of the fatal accidents in the desired years while *fars_map_state()* plots the observations of the given years in the provided state. The remaining functions (*fars_read()*, *make_filename()*, *fars_read_years()*) are called by these two functions and are also available for the user. The working directory should contain the observational data.


## Example data

The package provides data from the observations of years 2013, 2014, 2015 for practicing purposes.

## Examples

You can plot fatal accident data in Pennsylvania in 2013 by calling:
```{r example_1, eval = FALSE}
library(farspractise)
setwd(system.file("extdata",package = "farspractise"))
fars_map_state(39,2013)
```
Alternatively, you can get summarized data from observations in years 2013 - 2015 in all states of the USA by calling
```{r example_2, eval = FALSE}
fars_summarize_years(2013:2015)
```

Session info:

```{r sessioninfo}
sessionInfo()
```
